---
title: "Team 3 R Plots"
author: "Vishekha, Vincent, Nishi and Malik"
date: "11/12/2019"
output: html_document
---
# Analysis By Creating R Plots for pH level of water with respect to Dissolved Oxygen and Alkalinity For North Site.

## We would look at distribution for the variables Dissolved Oxygen, Alkanility and pH level of water for North site.


```{r}
# pH level's Distribution For North Site
hist(North_Site$pH,xlab=" pH level",ylab="Count", col="blue", main="pH level's Distribution For North Site", breaks=20)

```
### pH level shows normal distrubution with maximum number of samples lying between 7.5 to 8.5.


```{r}
#Dissolved Oxygen's Distribution For North Site
hist(North_Site$`Dissolved Oxygen`,xlab="Dissolved Oxygen",ylab="Count", col="blue", main="Dissolved Oxygen's Distribution For North Site", breaks=20)

```
### Dissolved Oxygen shows normal distribution with maximum number of samples lying between 0 to 18.


```{r}
#Alkalinity's Distribution For North Site
hist(North_Site$Alkalinity,xlab="Alkalinity",ylab="Count", col="blue", main="Alkalinity's Distribution For North Site", breaks=20)

```
### Alkanlinity shows normal distribution with maximum number of samples lying between 220 to 330.


## Box Plot for varibales Dissolved Oxygen and Alkalinity with and without outliers for North Site.

```{r}
#boxplot for Dissolved Oxygen with outlier for North Site
boxplot(North_Site$`Dissolved Oxygen`,main = "Boxplot for Dissolved Oxygen With Outlier")
#boxplot for Dissolved Oxygen without outlier
boxplot(North_Site$`Dissolved Oxygen`,outline=FALSE, main ="Boxplot for Dissolved Oxygen Without Outlier")
```
### From the above two graphs we conclude that the samples of Dissolved Oxygen contains Outliers.

```{r}
#boxplot for Alkalinity with outlier for West Site
boxplot(North_Site$Alkalinity,main = "Boxplot for Alkalinity with outlier")
#boxplot for Alkalinity without outlier
boxplot(North_Site$Alkalinity,outline=FALSE, main ="Boxplot for Alkalinity Without Outlier")
```
### From the above two graphs we conclude that the samples of Alkalinity contains Outliers.


## We would look at distribution for the variables Dissolved Oxygen, Alkanility and pH level of water for West site.

```{r}
# pH level's Distribution For West Site
hist(West_Site$pH,xlab=" pH leve",ylab="Count", col="blue", main="pH level's Distribution For West Site", breaks=20)

```
### pH level shows normal distrubution with maximum number of samples lying between 7.5 to 9.

```{r}
#Dissolved Oxygen's Distribution For North Site
hist(West_Site$`Dissolved Oxygen`,xlab="Dissolved Oxygen",ylab="Count", col="blue", main="Dissolved Oxygen's Distribution For West Site", breaks=20)

```
### Dissolved Oxygen shows normal distribution with maximum number of samples lying between 0 to 19.5.


```{r}
#Alkalinity's Distribution For North Site
hist(West_Site$Alkalinity,xlab="Alkalinity",ylab="Count", col="blue", main="Alkalinity's Distribution For West Site", breaks=20)

```
### Alkanlinity shows normal distribution with maximum number of samples lying between 230 to 320.


## Box Plot for varibales Dissolved Oxygen and Alkalinity with and without outliers for West Site

```{r}
#boxplot for Dissolved Oxygen with outlier
boxplot(West_Site$`Dissolved Oxygen`,main = "Boxplot for Dissolved Oxygen With Outlier")
#boxplot for Dissolved Oxygen without outlier
boxplot(West_Site$`Dissolved Oxygen`,outline=FALSE, main ="Boxplot for Dissolved Oxygen Without Outlier")
```
### From the above two graphs we conclude that the samples of Alkalinity contains Outliers.

```{r}
#boxplot for Alkalinity with outlier
boxplot(West_Site$Alkalinity,main = "Boxplot for Alkalinity with outlier")
#boxplot for Alkalinity without outlier
boxplot(West_Site$Alkalinity,outline=FALSE, main ="Boxplot for Alkalinity Without Outlier")
```
### From the above two graphs we conclude that the samples of Alkalinity contains Outliers.


## ggplot of variable pH for north and west site. 
We are trying to see the differences in pH value on the north and west site. As we know that water pH value lower than 7 is considered to be acidic and greater than 7 is considered to be basic. We can see from our graph the north site water was acidic in the years 2013 and 2017. West site water was acidic in the year 2014, 2016, and 2017. We can see there is a significant difference between north and west site water for pH value.

```{r}

ggplot (Nishi_dataset, mapping = aes(x = Year, y = pH, color = ObservationSite)) +geom_jitter()+ ggtitle ("pH value in north and west site")

```

## ggplot of variable E coli for North and West Site
We are trying to see the differences in Ecoli value on the north and west site. As we know that Ecoli value in water should not be exceeded 575 colonies per 100 ml of water. We can see from our graph that the bacteria E-coli was more than the standrad value in the west site compare to the north site.
```{r}

ggplot (Nishi_dataset, mapping = aes(x = Year, y = Ecoli, color = ObservationSite)) +geom_jitter()+ ggtitle ("pH value in north and west site")

```

