---
title: "Team 3 R Plots"
author: "Vishekha, Vincent, Nishi and Malik"
date: "11/12/2019"
output: html_document
---
# Analysis By Creating R Plots for pH level of water with respect to Dissolved Oxygen and Alkalinity For North Site.

## We would look at distribution for the variables Dissolved Oxygen and Alkanility and pH level of water for North site.

```{r}
# pH level's Distribution For North Site
hist(North_Site$pH,xlab=" pH level",ylab="Count", col="blue", main="pH level's Distribution For North Site", breaks=20)

```
### pH level shows normal distrubution with maximum number of samples lying between 7.5 to 8.5.


```{r}
#Dissolved Oxygen's Distribution For North Site
hist(North_Site$`Dissolved Oxygen`,xlab="Dissolved Oxygen",ylab="Count", col="blue", main="Dissolved Oxygen's Distribution For North Site", breaks=20)

```
### Dissolved Oxygen shows normal distribution with maximum number of samples lying between 0 to 18.


```{r}
#Alkalinity's Distribution For North Site
hist(North_Site$Alkalinity,xlab="Alkalinity",ylab="Count", col="blue", main="Alkalinity's Distribution For North Site", breaks=20)

```
### Alkanlinity shows normal distribution with maximum number of samples lying between 220 to 330.


## Box Plot for varibales Dissolved Oxygen and Alkalinity with and without outliers for North Site.

```{r}
#boxplot for Dissolved Oxygen with outlier for North Site
boxplot(North_Site$`Dissolved Oxygen`,main = "Boxplot for Dissolved Oxygen With Outlier")
#boxplot for Dissolved Oxygen without outlier
boxplot(North_Site$`Dissolved Oxygen`,outline=FALSE, main ="Boxplot for Dissolved Oxygen Without Outlier")
```
### From the above two graphs we conclude that the samples of Dissolved Oxygen contains Outliers.

```{r}
#boxplot for Alkalinity with outlier for West Site
boxplot(North_Site$Alkalinity,main = "Boxplot for Alkalinity with outlier")
#boxplot for Alkalinity without outlier
boxplot(North_Site$Alkalinity,outline=FALSE, main ="Boxplot for Alkalinity Without Outlier")
```
### From the above two graphs we conclude that the samples of Alkalinity contains Outliers.



## We would look at distribution for the variables Dissolved Oxygen and Alkanility and pH level of water for West site.

```{r}
# pH level's Distribution For West Site
hist(West_Site$pH,xlab=" pH leve",ylab="Count", col="blue", main="pH level's Distribution For West Site", breaks=20)

```
### pH level shows normal distrubution with maximum number of samples lying between 7.5 to 9.

```{r}
#Dissolved Oxygen's Distribution For North Site
hist(West_Site$`Dissolved Oxygen`,xlab="Dissolved Oxygen",ylab="Count", col="blue", main="Dissolved Oxygen's Distribution For West Site", breaks=20)

```
### Dissolved Oxygen shows normal distribution with maximum number of samples lying between 0 to 19.5.


```{r}
#Alkalinity's Distribution For North Site
hist(West_Site$Alkalinity,xlab="Alkalinity",ylab="Count", col="blue", main="Alkalinity's Distribution For West Site", breaks=20)

```
### Alkanlinity shows normal distribution with maximum number of samples lying between 230 to 320.


## Box Plot for varibales Dissolved Oxygen and Alkalinity with and without outliers for West Site

```{r}
#boxplot for Dissolved Oxygen with outlier
boxplot(West_Site$`Dissolved Oxygen`,main = "Boxplot for Dissolved Oxygen With Outlier")
#boxplot for Dissolved Oxygen without outlier
boxplot(West_Site$`Dissolved Oxygen`,outline=FALSE, main ="Boxplot for Dissolved Oxygen Without Outlier")
```
### From the above two graphs we conclude that the samples of Alkalinity contains Outliers.

```{r}
#boxplot for Alkalinity with outlier
boxplot(West_Site$Alkalinity,main = "Boxplot for Alkalinity with outlier")
#boxplot for Alkalinity without outlier
boxplot(West_Site$Alkalinity,outline=FALSE, main ="Boxplot for Alkalinity Without Outlier")
```
### From the above two graphs we conclude that the samples of Alkalinity contains Outliers.



## Histogram of variables pH, and Ecoli for North and West site
```{r}
hist(siteData$North$pH)
hist(siteData$North$`E. coli`)
hist(siteData$West$pH)
hist(siteData$West$`E. coli`)
```

## Boxplot of variables pH, and Ecoli for North and West site
```{r}
boxplot(siteData$North$pH)
boxplot(siteData$North$`E. coli`)
boxplot(siteData$West$pH)
boxplot(siteData$West$`E. coli`)
```

## Plots for ph aganist E coli for North and West Site
```{r}
plot(siteData$North$pH ~ siteData$North$`E. coli`)
plot(siteData$West$pH ~ siteData$West$`E. coli`)
```

