---
title: "Team 3 R Plots"
author: "Vishekha, Vincent, Nishi and Malik"
date: "11/12/2019"
output: html_document
---
# Analysis By Creating R Plots for pH level of water with respect to Dissolved Oxygen and Alkalinity For North Site ---------------

## We would look at distribution for each of the variables

```{r}
# pH level's Distribution For North Site
hist(North_Site$pH,xlab=" pH leve",ylab="Count", col="blue", main="pH level's Distribution For North Site", breaks=20)

```

```{r}
#Dissolved Oxygen's Distribution For North Site
hist(North_Site$`Dissolved Oxygen`,xlab="Dissolved Oxygen",ylab="Count", col="blue", main="Dissolved Oxygen's Distribution For North Site", breaks=20)

```

```{r}
#Alkalinity's Distribution For North Site
hist(North_Site$Alkalinity,xlab="Alkalinity",ylab="Count", col="blue", main="Alkalinity's Distribution For North Site", breaks=20)

```

## Box Plot for varibales Dissolved Oxygen and Alkalinity with and without outliers for North Site

```{r}
#boxplot for Dissolved Oxygen with outlier for North Site
boxplot(North_Site$`Dissolved Oxygen`,main = "Boxplot for Dissolved Oxygen With Outlier")
#boxplot for Dissolved Oxygen without outlier
boxplot(North_Site$`Dissolved Oxygen`,outline=FALSE, main ="Boxplot for Dissolved Oxygen Without Outlier")
```

```{r}
#boxplot for Alkalinity with outlier for West Site
boxplot(North_Site$Alkalinity,main = "Boxplot for Alkalinity with outlier")
#boxplot for Alkalinity without outlier
boxplot(North_Site$Alkalinity,outline=FALSE, main ="Boxplot for Alkalinity Without Outlier")
```

# We would look at distribution for each of the variables

```{r}
# pH level's Distribution For North Site
hist(West_Site$pH,xlab=" pH leve",ylab="Count", col="blue", main="pH level's Distribution For West Site", breaks=20)

```

```{r}
#Dissolved Oxygen's Distribution For North Site
hist(West_Site$`Dissolved Oxygen`,xlab="Dissolved Oxygen",ylab="Count", col="blue", main="Dissolved Oxygen's Distribution For West Site", breaks=20)

```

```{r}
#Alkalinity's Distribution For North Site
hist(West_Site$Alkalinity,xlab="Alkalinity",ylab="Count", col="blue", main="Alkalinity's Distribution For West Site", breaks=20)

```

## Box Plot for varibales Dissolved Oxygen and Alkalinity with and without outliers for West Site

```{r}
#boxplot for Dissolved Oxygen with outlier
boxplot(West_Site$`Dissolved Oxygen`,main = "Boxplot for Dissolved Oxygen With Outlier")
#boxplot for Dissolved Oxygen without outlier
boxplot(West_Site$`Dissolved Oxygen`,outline=FALSE, main ="Boxplot for Dissolved Oxygen Without Outlier")
```

```{r}
#boxplot for Alkalinity with outlier
boxplot(West_Site$Alkalinity,main = "Boxplot for Alkalinity with outlier")
#boxplot for Alkalinity without outlier
boxplot(West_Site$Alkalinity,outline=FALSE, main ="Boxplot for Alkalinity Without Outlier")
```

## Histogram of variables pH, and Ecoli for North and West site
```{r}
hist(siteData$North$pH)
hist(siteData$North$`E. coli`)
hist(siteData$West$pH)
hist(siteData$West$`E. coli`)
```

## Boxplot of variables pH, and Ecoli for North and West site
```{r}
boxplot(siteData$North$pH)
boxplot(siteData$North$`E. coli`)
boxplot(siteData$West$pH)
boxplot(siteData$West$`E. coli`)
```

## Plots for ph aganist E coli for North and West Site
```{r}
plot(siteData$North$pH ~ siteData$North$`E. coli`)
plot(siteData$West$pH ~ siteData$West$`E. coli`)
```

